Constraint Programming - Inside Gecode

### 2014-05-03 paper.tex
search algorithms

	\subsubsection{Limited Discrepancy Search}

>>>>

	\subsubsection{Limited Discrepancy Search}
	Limited Discrepancy Search is a variation of a more general Best-First Search and was first mentioned by Harvey and Ginsberg \cite{limitedDiscrepancy}. The basic concept is that during the iteration through a search tree it is better, in terms of execution time or, more formal, complexity, to fail closer to the root. If one constraint fails very close to the root only litte effort was put into this branch.
